Determinism, Complexity, and Predictability in Computer Performance

### 2014-05-30 pecomplexity.tex
add preprint info

\vspace{0.1in}
\noindent
{\bf Keywords}: entropy, permutation entropy, weighted permutation
entropy, time-series analysis, predictibility

>>>>

\vspace{0.1in}
\noindent
{\bf Keywords}: entropy, permutation entropy, weighted permutation
entropy, time-series analysis, predictability

\preprint{Santa Fe Institute Working Paper XX-XX-XXX}
\preprint{arxiv.org:XXXX.XXXX [nlin.CD]}
